Transforming Trash as an Artistic Act

### 2015-12-06 chapter1_reduced.tex
Reduction
Former-commit-id: c287ed58ed0af64082641437043495694a05ba72

%****************************************
% Structure of this chapter
% Section: explain the topic and its significance, raise curiosity, give some facts about it.
% Section: state the the purpose of this study, specify the focus of it.
% Section: overview of chapters and structure of thesis.
% Section: a note on terminology, clarification about the comprehensive terminology.
%........................................

%****************************************
% Sample phrases:
% The discussions (mentioned discussion are also formed the thesis project entitled ... )
% Aim of this thesis is ...
% There has been a recent spate of artistic work focusing on (over-)consumption using the lens of disposal and discard.
% as a reaction to the consumerist society.
%........................................

@@

%****************************************
% Rubbish: the archaeology of garbage. rathje1992rubbish
% Garbage project's findings have supplied a fresh perspective on what we know --- and what we think we know --- about certain aspects of our lives. p.24

% The basic methods of garbage disposal are four: dumping it, burning it, turning it into something that can be useful (recycling), and minimizing the volume of material goods.(p.33)

% ancient peoples p.33

% fast food packaging. p97

% human behavior p.55 can you tell a lot about the customers from their garbage?

%p191-192 people tend to think of "recycling" as a relatively modern conceit that has only recently gained broad public acceptance, and whose practical benefits have only just began to be realized. Recycling itself is probably as old as --- indeed, seems to be a fundamental characteristic of --- human species.

%p.209 The reuse of paper, for example, involves processes that generated a considerable amount of hazardous waste. In order to recycle newspapers, magazines, and, indeed, any printed paper, the paper must first be de-inked. At the end of the de-inking process one is left with essentially two products: on the one hand, de-inked fiber that will be turned into new paper; and on th other, a large quantity of toxic sludge.
%........................................

%****************************************
% trasformations

% during great depression, I learned firsthand about frugality as a child during ww2. my family carefully folded the wrapping paper from gifts to reuse on other occasions. p.8

% p11. for decades we've taken for granted used cars and old houses. Is there anyone alive who has always lived in new houses or driven only new cars?

% p.11 Economics has always been a factor in recycling.

% p.12 recycling is not limited to folk art.

% Bicycle wheel duchamp 1913.

% Use of recycled materials is not new, not is it exclusive to the united states. p.18

% p.22 Material, meaning, and memory --- these are artists' reasons for using found objects.

% p.48 recycling may be the most wasteful activity in modern America --- a waste of time and money, a waste of human and anutral resources. john tierney, "What a Waste," seattle postintelligencer...
%........................................

Common perception to the trash is to get rid of it as soon as possible. People want to depose trash from their lives most of time not thinking beyond. However to establish solid understanding of trash, we have to give attention to the trash and ask why it is trash? How does it become trash?

\paraphrase{Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others. The names we give this material ---waste, garbage, refuse, trash, rubbish--- have pejorative definitions. Worthless. Rejected and useless matter of any kind. Unimportant. Our trash is a testament; what we throw away says much about our values, our habits, and our lives. While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared. \ldots the question of who owns these discards is not trivial. The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream. Our trash is part of us, whether or not we choose to acknowledge it \cite{zimring2012encyclopedia}}. \todo{ref for tracey emin et al.}

In this thesis work to understand the different aspects of trash is a key element. \todo[inline]{These aspects are \ldots} As scholars agreed on \todo{ref.} it is part of our life and daily practice and it is very common concepts from developed cities to rural areas, from modern societies to ancient societies. Sometimes it is accepted as a problem (waste crises, ecological problems.) that is need to carefully and seriously managed. On the other hand it is accepted as a source of diversity. (To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?) or aspects). Therefore we should ask these questions: What is trash? How does it became trash? Is it a end product or a source material? How much is it valuable? How much is it dangerous?

%\comment{In previous ages (which age? pre industrial ages?) objects and resources are used again and again. Production of objects are hard and laborious. Böyle çok fazla kullanılan nesneye örnek bulsak ne kadar güzel olur. Mendillere bunlara örnek olabilir. Aslında tam benim konumla ilgili çünkü tek kullanımlık. Hijyen kavramıyla ilgili giderek artan da bir ilgi necesiyle tek kullanımlık peçeteler gittikçe önem kazanıyor. Peki burda illaha geçmişe falan girmek gerek var mı? çok mu derdimde benim?}

%\comment{Dört bir yanımız metalarla çevrilmş durumda, istediğimiz şeylere çok kolay bir şekilde ulaşabiliyoruz. Yemek siparişi veriyoruz ayağımıza geliyor. İki blok ötedeki kahveciden istediğimiz zaman kahvemizi alıyoruz. Ama tüm bunların bir bedeli var. Bir yandan da sürekli olarak çöp üretiyoruz. Her ne kadar son derece sistemli bir şekilde çöpler toplanıyor ve belki de ne kadar tüketildiğini hiçbir zaman farkına var mıyoruz?}

% Trash is everywhere and, produced every time
Modern (developed) societies are continuously generating trash and, pile them on landfills. During daily activities (drinking, eating, waiting in the bank?) trash is generated and people get rid of them as quickly as possible. (Various objects become trash after their primary functions consumed. People do not care the package of the objects that they buy. They buy the coffee not the cup of it. After coffee finished the life of cup also finishes. Very small life. But is that really so? Is that really life of an object ends after tossed on the waste bin? \todo{Rubbish Theory, Zizek} (Objects life time in the nature is more than human being. People use them for just 5minutes, however they will exist years on the nature.) The vast amount of industrial discarded items spread through the landfills to oceans. They are the result of highly complex industrial production methods. \comment{They are not easily disposable items in the nature.} They live in the nature thousands of years. They are durable(in terms of resistant to natural affects) products. Most of them packages that are used to carry or protect other materials. After real material used these packages became valueless (or useless). (types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?  This is the common approach to trash and the main problem. (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc. (Instead of creating new opportunities or alternatives, it is a consuming all of them (which?) and producing huge pile of trash.)

\textbf{Trash is global}, and shared concept for all societies throughout the ages. 
\textbf{Trash in every age.} In other words it is part of human activity of every historic age. It exists early ages of human to now. Trash is part of the early days of human production / or activity. Archaeologist find things from people throw away. 
\textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
\textbf{Trash is everywhere.} in the streets, in your home, in the sea that you swam, around the globe \todo{satellite discard covers the atmosphere}. Even if trash is isolated by people, it is close as closest waste bin.

[RELATIVE] As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}. She realized that any of them called the practice as recycling. For them using trash again and again is very natural and it is part of their life. On the contrary for the developed countries trash considered as a thing that must be avoided. There is no place for trash in their life. It can be understood that approach to the trash is not same for the all regions of world \todo{ref}.

% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
% TODO PRAP.
[FACTS] \paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD\footnote{OECD(Organization for Economic Co-operation and Development) is an international economic organization of 34 countries. Turkey is member of this organization.} countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.} \todo{Zengin adamın harcama lüksü}

% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
% TODO PRAP.
\paraphrase{\textbf{We relate to garbage daily. We use it, produce it and dispose of it. Endlessly. The most obsessive of us get rid of it as fast as we can.} The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes. We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations). Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding. Particularly in the connection between garbage and the arts, \textbf{I am interested in two questions. First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material} \cite{ibarra2015beautiful}.}

People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore. However is it really values? What does make it valueless?

People do not think what happens after they throw it away. It exits from your life but not the world. What happens when you throw it away? It is stacked from another place. Value of objects are not static. Trash is not static \todo{ref. first paragraph.} also it has a long journey. A project conducted by MIT researches journey of trash by placing trackers onto the trash \cite{chen2009mit}. The results are surprising. Trashes spread away across the country and this journey takes month. \todo[inline]{give exact reference} We know that it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo[inline]{footnote what are these countries?}. In other worlds Americans trash is not only their trash. As commodities spread to the every corner of the world, trash also. What happens when it is traveled to the other countries, how they approaches these items. \comment{They find new uses and meanings on them.} \todo[inline]{consider Papua genen people}

\begin{quote}
\paraphrase{“Nobody wonders where, each day, they carry their load of refuse. Outside the city, surely; but each year the city expands, and the street cleaners have to fall farther back. The bulk of the outflow increases and the piles rise higher, become stratified, extend over a wider perimeter” – Italo Calvino, Invisible Cities} The project is an initial investigation into understanding the 'removal-chain' in urban areas and it represents a type of change that is taking place in cities: a bottom-up approach to managing resources and promoting behavioral change through pervasive technologies. TrashTrack builds on previous work of the SENSEable City Lab in its exploration of how the increasing deployment of sensors and mobile technologies radically transforms how we understand and describe cities. “People just take their trash and put it on the curb and they forget about it and don’t think about all the time and energy and money put into disposing of it.”
\end{quote}

% Cycle of trash
Trash moves, objects moves from place to place. From homes to garbage trucks. From streets to land fills. From garbage baskets to sculptures. \todo[inline]{REF. MIT Garbage project} Lots of different people touches to trash. With the trash what moves?

% ARTWORK http://timgaudreau.com/2012/trash/trash.html
[ARTWORK] \comment{Self-Portrait as Revealed by Trash} Even if people pay little attention, everybody do not. An artist takes photos of his every trash, like people take photos of their faces. He focuses on the thing that paid little attention, that is trash. At the end he exhibits all the photos by covering all the walls of room. It can seen as record of his activities, record of commodities. Most of them we are not aware of them. Draw the attention of is being thrown away and every time and everywhere. They are too much and can only fit covering all the walls. \todo[inline]{Tim Gaudreau “Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006”} \paraphrase{After photographing my trash over the course of the year, I ended up with 5,000 images representing my waste stream. These collections of grids represent my first experiments with using those images. This initial work ultimately led to the full scale collages that have become my Self-portrait as Revealed by Trash: 365 days of photographing everything I threw out.}

% ARTWORK http://www.keaggy.com/chairs/sad/12/
\todo[inline]{Sad chair. Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.}

Why people are interested in rubbish. Some of the artist also interested in others trash. \comment{O çöplerde ne bulmayı umuyorlar ki? Aslında çöp bizim davranışlarımız, yaşayız tarzımız hakkında bize yön veriyor. ve bu her zaman fiziksel dönüştürme ile değil de aynı zamanda anlamsal ve mekansal değiştirme sorulamalarla mümkün oluyor. Bazen de olduğu gibi kullanıyorlar. bu açıdan önemli. Çöpü çöp şekliden sunan sanatçılar. Ama bu nasıl mümkün ki? fotoğrafını çekenler aslında gerçekten ona müdahele etmemiş mi oluyorlar. Bence değil? bir şekilde müdahele var gene orada. o fotoğraflarda artık dikkatin objesi haline geliyor. çöpün dönüşmesi aslında bir diğer yandan çöpe bakışın değişmesi olarak görülebilir.}

% TODO Life time of objects.
% Nesnelerin yaşam süreleri... Can you imagine how much plastic cup is being consumed every hour?

@@

This trash phenomena catches the attention of artist. It is very human activity. In this context which trash? What type of discard. Human discard. trashes of human activity. items that belongs to human. commodities etc.

%****************************************
% EVERYTHING CAN BE TRASH. Act of trashing not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
% Michael Landy's Art Bin uses a art gallery to create his dust bin. Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed. Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints. "There's no hierarchy once they are in the bin" All of them are accepted as same. Ultimate equality. Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts. Nothing's too good for the art bin. Everything can fit into the art bin. Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art. As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”. It is a very big glass bin and isolates people. There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin". There is no limitation of throwing away even if art.

% Herkes çöpü dönüştürmüyor, bazıları ise çöpe dönüştürüyor. Ama ben bununla ilgilenmiyorum aslında.
%........................................

\todo[inline]{ArtBin, squeezing. [Trashing Things, Artwork]}

%http://www.smithsonianmag.com/arts-culture/photographer-creates-fine-art-out-trash-we-throw-environment-180951615/?no-ist
\todo[inline]{showing trash as they are... [Artwork] by Barry Rosenthal}

%****************************************
% Different types of trash
\todo[inline]{Different types of trash.} \comment{There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.}

The complexity of produced trashes of societies is increasing. For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies. Think batteries and so on. Every society generates different types of wastes. Differs from country to country, society to society, ages to ages. It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase. Therefore for the ones that have no complex tools it is becoming harder to reuse objects. In other words objects become more complex their re-usage becomes less likely.  Different production process generates different types of trash. According to production process, decomposition process\ldots The approach to the different type of trash will be different. In other word if trash is a result of classification of objects, it can be easily extracted that there is classification inside of it. There are some trashes that are more close to the people. More easy to convert them. more easy to regain to the society. 
%........................................

%****************************************
% Different disciplines, Perspectives related with trash from different disciplines
\todo[inline]{List of disciplines, and their approach to the trash.} \comment{Trash draws attention different peoples and disciplines. In other words there are different studies related with trash. Different approaches to the trash and son on.}

% From Trashion: The Return of Disposed, Bahar Emgin.
\paraphrase{Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture.}

This is very important because the problem of trash is being tried to be handled by different disciplines. In other words there different approaches to the trash. Different problems, different solutions. Which perspective that I have. In what ways my project differs from them. The purpose is to participate people in this work, by collecting them etc. And also offer to transform it. Rescue it and than later transform it. In short, the difference between the other disciplines must be clear. 
\begin{itemize}
\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
\item Management of it (handled by the municipals generally).
\item Technological perspectives. (seeing trash as a design problem. developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed? development in what sense?)
\end{itemize}

\comment{Trash draws attention of many scholars and people who are professional in different areas. Further trash is a common subject of the all ages through the human history. In other words this topic is not introduced in recent years (or ages). It always part of the human practice and life. Even if trash is refused and discarded thing, there are people giving attention to them.}
%........................................

%%%
%%%
%%%
\section{Purpose of the Study}
\todo[inline]{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}

@@

In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored. Why and how are they used by the artist? Are there any differences with the original items compared to discarded items? Has using discarded material or trash specific (or special) meaning and message? This is a work to explore the re-usage of trash in artworks (place or the role in the art practice). (and also in which scope? medium, message, life practice\ldots)

@@

\comment{How does it become trash?} Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a road map (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods? Therefore first question is why they are less-valued, and ignored. How to make them valuable? How to make them part of our life again?)

%%%
%%%
%%% 
\section{Structure of the Study}
This study is structured by many examples of artworks in different part of the thesis. When a topic or argument is presented, immediately example artwork is given at this moment and how artist replies this issue is illustrated. Thereby artworks are examined in the theoretical and cultural context. Artworks are used as a supportive elements for the stated arguments.  However, not every time artworks are discussed in detail. Only basic information is given and how it is related with this topic explained. \comment{By the way} it is better to keep in mind that all works can be analyzed in different contexts in more detail fashion.

Following chapter, Trash in Culture and Theory, explores the place of trash in the cultural life and theoretical approaches on trash. The aim is (better) to understand the trash in cultural and theoretical aspects. (to better realization the notion of trash.) Provides theoretical and cultural background. It is explored the trash is being worked is whose trash. Or what type of society generate this trash. Also in the project I collect the paper trash. What type of approach generate it and what are the dynamics of it? What type of trash we are talking about? It is understood through the patters of consumption patterns. And to reflect this cultural phenomena what philosophers and scholars say. Artist how they are reflected this notion.and also looked how scholars are conceptualized trash and its movement on the different values system. How explained the transient nature of trash?

@@

\comment{Fourth chapter consists of the overview of the project. Stated the approach to topic clearly. Development process of the work is presented in detail. I will start with the development process of the work. I believe that the way an artist works and the obstacles that she encounters have a huge impact on how the final work is embodied. Development process of my work shaped the way I think on the subject of my thesis. Therefore, I will explain my process as detailed as possible. Then, I will continue with different aspects of my work; formal decisions and usage of light that I believe carry my work to another level. At the end of this chapter, we will see how my work functions and what it proposes on the image and word relationship.}

\comment{Finally last chapter is reserved for an overall conclusion of this thesis and further suggestions on the subject and the project.}

%%%
%%%
%%%
\section{A Note on Terminology}
Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash. Analysis of them may be subject of another thesis. (Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash. Although there are slight differences between these words, sometimes they are used to signify same concept (or used with same purposes). Understanding diverse vocabulary of this topic before dive into the theory makes more clearer the borders of the work. There is no consensus on terminology. Some scholars uses junk art, others recycling art. The origin of vocabulary of this topic reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined? From the rubbish: the archeology of garbage gives clearer definition of some these words:

@@

Some notes on methods:

%****************************************
% Reuse and Recycle
One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars \todo{ref}

According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form. Reusing lengthens the life of the item or material. Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others. The main purpose is to make the item last as long as it can. To reuse is to use something again instead of throwing it away or sending it off to a recycling company. \textbf{Why throw something away when you can give it another life?} Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product. Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose. For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.

According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product. It is an energy consuming process. For example, if we put some plastic bottles, paper, or aluminum items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt. In this process, energy is required which depends upon the stages of transformation.

Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product. Examples are crushed glass containers (cullet) used to make new glass containers, and scrap metal used in foundries.

>>>>

@@

%
%
[Every.] \paraphrase{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others \cite{zimring2012encyclopedia}.}

Trash in every age and every society. Refuse is part of people's consumption practices and it is very common concept from developed cities to rural areas, from modern societies to ancient societies\cite[p.33]{rathje1992rubbish} \todo{more ref.}. For archaeologist dumps are one the significant places to figure how people consume in the ancient times \todo{ref}.

Trash is everywhere and, produced every time. During daily activities such as drinking coffee, eating beverages, waiting in the bank trash is generated. The pattern is spread to the all day and different places. It is hard to say that any location(place) is waste free. Nearly every place people require waste bin. If we do not find a waste bin, people often leave it (to the ground?). Production of trash never stops.

Trash is everywhere. Trash is in the streets, in your home, in the sea that you swam, rotating around the globe \footnote{Satellite discards leaved the atmosphere and they rotate around the globe like satellites.}. Even if trash is tried to be moved away from people life, it is close as closest waste bin.

%
%
% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
[Facts.] \paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD\footnote{OECD(Organization for Economic Co-operation and Development) is an international economic organization of 34 countries. Turkey is member of this organization.} countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.} \todo{Zengin adamın harcama lüksü}

\comment{Bunu neden diyorsun? Teze nasıl bir katkı sağlıyor?}

%
%
[Common.] (In the dictionary \todo{Which dictionary?} trash means anything useless, worthless or discarded. In parallel to this definition, common perception is to get rid of them as soon as possible. People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore. People want to refuse them from their lives most of the time not thinking beyond (or alternative). However to establish solid understanding of trash (or trashing things), we have to give attention to the trash (and ask why it is trash). \comment{(To understand the beyond common perception we have to ask...)} How does it become trash? \comment{Is it possible to do something other than refusing them?}

Instead of creating new usages, combinations or alternatives, common approach is to ignore all the possibilities embedded to the trash. People do not see beyond the primary function.

%
%
[Moves.] The vast amount of industrial discarded items spread through the landfills to oceans.

Trash moves, objects moves from place to place. From homes to garbage trucks. From streets to land fills. From garbage baskets to sculptures. Lots of different people touches to trash. With the trash what moves? Trash moves around. Travels like humans. Travels like commodities. When we are telling about the travel of commodities, then it is easy to say that trashes also moves around.

People do not think what happens after they throw trash away. \paraphrase{They forget about it and don’t think about all the time and energy and money put into disposing of it.} It exits from people's life but not the world. It is stacked to another place.

A project conducted by MIT researches journey of trash by placing trackers onto the trash \cite{chen2009mit}. The results are surprising. Trashes spread away across the country and this journey takes month. Further it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo[inline]{footnote what are these countries?}. In other words American's trash is not only their trash. As commodities spread to the every corner of the world, trash also. What happens when it is traveled to the other countries, how they approaches these items. \comment{They find new uses and meanings on them.} \todo[inline]{consider African native}

%
%
[Aspects. Approaches.] In this thesis study to understand the different aspects of trash is a key element. Sometimes it is accepted as a problem (for examples keeping streets clean, handling the smell) that is need to carefully and seriously managed. On the other hand it is accepted as a source of diversity. Further for the recyclers it is a source of income. The economical aspect of trash can not ignored. There are people who collects plastics, scraps and papers from waste bins and landfills. By collecting and selling them they endure their life. Further some of the countries \todo{ref.} imports garbage to recycle or use their own purposes. As it can be seen clearly there are different aspects and approaches to the trash. For some people it is disgusting thing and moved away from living space and for the others source of their life. \paraphrase{While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared \cite{zimring2012encyclopedia}.}

[Relative.] As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}. She realized that any of them called the practice as recycling. For them using trash again and again is very natural and it is part of their life. On the contrary for the developed countries trash considered as a thing that must be avoided. There is no place for trash in their life. It can be understood that approach to the trash is not same for the all regions of world \todo{ref}.

% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
\paraphrase{We use it, produce it and dispose of it \cite{ibarra2015beautiful}. The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes \cite{ibarra2015beautiful}.}

[Production of trash and removal of trash.] For example a project conducted by MIT Sensible City Lab. reveals the \quotes{removal-chain} of objects by tracking trash with the mobile trackers places onto the trash \cite{chen2009mit}.

%
%
[Parts of us.] \paraphrase{Our trash is a testament; what we throw away says much about our values, our habits, and our lives \cite{zimring2012encyclopedia}. Our trash is part of us, whether or not we choose to acknowledge it \cite{zimring2012encyclopedia}. The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream \cite{zimring2012encyclopedia}.}

%
%
[Change in the production and consumption practices.] \paraphrase{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption. Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.} As the result of it amount of goods boost and the cost of them significantly reduced. Things once reused again and again, now thrown away because it is more affordable to replace \todo{daha uygun bir kelime bul} with new one. \paraphrase{Mass production and commodification liquidated what remained of folkways tied to local production, demanding people construct the meaning of their lives through purchases rather than production. (FROM Collage Culture)} As the production increased its by-product material waste is also increased. \paraphrase{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption. (Trash Culture)} \todo{Ref: Trash Culture}

%
%
[Current] During the last decades much attention has been devoted to the waste. In particularly environmental considerations dominates the perceptions of waste.

% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
\paraphrase{Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding \cite{ibarra2015beautiful}.}

%
%
[Art] \paraphrase{At least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art.} \todo{Bu nereden?}

@@

%
%****************************************
\section{Purpose of the Study}
% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
\paraphrase{Particularly in the connection between garbage and the arts, I am interested in two questions. First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material \cite{ibarra2015beautiful}.}

Some of the artist also interested in others trash. Why people are interested in rubbish?

\todo[inline]{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}

@@

In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored. Why and how are they used by the artist? Are there any differences with the original items compared to discarded items? Has using discarded material or trash specific (or special) meaning and message?

\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature.}

%
%
[Different types of trash] There are different types of trashes. Result of different production and consumption practices different trashes are generated. For example \paraphrase{radioactive waste is usually a by-product of nuclear power generation and other applications of nuclear fission or nuclear technology}. Electronic waste (e-waste), Construction and demolition waste, Medical waste are one of them. As it can be seen that there are lots of different types and as various as activities of human. In this scope of thesis \ldots \todo{Ben hangisini kullanacağım. Buna burada değinmek gerekli mi?}

%
%
[Different disciplines of trash] Trash draws attention different peoples and disciplines.

% From Trashion: The Return of Disposed, Bahar Emgin.
\paraphrase{Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture.} \todo{ref.}

Increasing ecological concerns is one of the aspects of trash. As most of trash last decades are not easily decomposable. Relases toxics and other things.

Technological perspectives. (seeing trash as a design problem. developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed? development in what sense?)

Management of it (handled by the municipals generally). Removal from the life spaces of human.

@@

%
%
[Scope] Human discard. In the scope of trash not biodegradable trash is considered. Produced, industrial commodities are considered.

%
%****************************************
\section{Structure of the Study}
Theory and artworks are not strictly separated from each other. Artworks are explained with the help of theories. This study is structured by many examples of artworks in different part of the thesis. When a topic or argument is presented, immediately example artwork is given at this moment and how artist replies this issue is illustrated. Thereby artworks are examined in the theoretical and cultural context. Artworks are used as a supportive elements for the stated arguments.  However, not every time artworks are discussed in detail. Only basic information is given and how it is related with this topic explained. By the way it is better to keep in mind that all works can be analyzed in different contexts in more detail fashion.

% TODO Move to chapter 4.
\comment{Research and the found samples of works helped a lot to shape my work. They provide me deeper understanding of the subject and what I am doing and they lead me during the development of the work.}

Following chapter, Trash in Culture and Theory, explores the place of trash in the cultural life and theoretical approaches on(of?) trash. The aim is to understand the trash in cultural and theoretical aspects. (Better realization the notion of trash) Chapter 2 provides theoretical and cultural background. It is explored the trash is being worked is whose trash. Or what type of society generate this trash. What type of approach generate it and what are the dynamics of it? What type of trash we are talking about? It is understood through the patters of consumption patterns. And to reflect this cultural phenomena what philosophers and scholars say. Artist how they are reflected this notion.and also looked how scholars are conceptualized trash and its movement on the different values system. How explained the transient nature of trash?

@@

Fourth chapter consists of the overview of the project. Stated the approach to topic clearly. Development process of the work is presented in detail. It will start with the development process of the work. I believe that the way an artist works and the obstacles that she encounters have a huge impact on how the final work is embodied. Development process of my work shaped the way I think on the subject of my thesis. Therefore, I will explain my process as detailed as possible. Then, I will continue with different aspects of my work; formal decisions and usage of light that I believe carry my work to another level. At the end of this chapter, we will see how my work functions and what it proposes on the image and word relationship. \todo{rewrite, copy paste from another thesis.}

Finally last chapter is reserved for an overall conclusion of this thesis and further suggestions on the subject and the project.

%
%****************************************
\section{A Note on Terminology}
Many scholars and authors have used different words (or terminology) to define trash\todo{bunun yerine başka bir şey demek gerekir mi?}. Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter are some of them. Although there are slight differences between these words, sometimes they are used to signify same concept (or used with the same purposes). It signifies that the topic is so broad and there is no consensus on terminology. Words are used interchangeably. From the book \quotes{Rubbish: the Archeology of Garbage} gives clearer definition of some these words:

@@

From another book (Trash Culture):
\paraphrase{Literature of trash feature a broad range of terms, reflecting the multifaceted and conceptually complex nature of the issue at hand. Many of these terms --- such as ‘trash’, ‘garbage’ and ‘rubbish’ --- are frequently used interchangeably. This is not least because the variety of terms reflects the variations in English and US vocabulary and thus all usages are retained as individual authors intended in order to reflect the international nature of this volume. Other related terms, such as ‘ruins’, ‘obsolete’, ‘waste’, ‘discards’ are used in a variety of contexts in each chapter. Again, these usages have been retained to reflect the focus of individual studies.}

In addition to these there is also confusion of the terms: reuse and recycling which are the (general) methods transforming trash to the another thing. Both of them are used widely by scholars.

\paraphrase{According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form. Reusing lengthens the life of the item or material. Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others. The main purpose is to make the item last as long as it can. To reuse is to use something again instead of throwing it away or sending it off to a recycling company. \textbf{Why throw something away when you can give it another life?} Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose. For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.} Reusing is possible with re seeing (rethinking). Reusing is possible meet the needs of the human itself. Using creativity and personal approach can change objects functions. It is possible to use objects for different purposes.
